### 2024-04-08 README.qmd
Update readme

@@

```{r}
table(d$offence) |>
  sort()
```

```{r}
d |>
  # Reduce nchar of offence
  mutate(offence = stringr::str_sub(offence, 1, 60)) |>
  group_by(offence) |>
  # Count number of rows in each group
  mutate(n = n()) |>
  filter(n > nrow(d) / 50)|>
  ggplot() +
  geom_bar(aes(offence)) +
  # Make x labels vertical
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

>>>>

We provide a function to geocode the records:

@@

You can query the data downloaded with `opsnap` functions, e.g. as follows (results not shown):

```{r}
#| eval: false
table(d$offence) |>
  sort()
```

Let's make a plot of the data:

```{r}
d |>
  # Reduce nchar of offence
  mutate(offence = stringr::str_sub(offence, 1, 60)) |>
  group_by(offence) |>
  # Count number of rows in each group
  mutate(n = n()) |>
  filter(n > nrow(d) / 50)|>
  ggplot() +
  geom_bar(aes(offence)) +
  # Make x labels vertical
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
